---
title: "Basic Usage of the `plantuml` package"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic Usage of the `plantuml` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(plantuml)
```

# Overview
This package provides the functionality to create UML graphs using the [PlantUML](http://plantuml.com/) language.

# Installation of plantuml binary
The package does not come with the plantuml binary, which needs to be installed as well. repeated calling of this function updates the binary.
```{r installation_plantuml, eval = TRUE}
plantuml_update()
```

# Plotting Plantuml graphics
## Define plantuml code
First, we define a plantuml object based on some plantuml code 
```{r definePlantuml}
library(plantuml)
x <- '
(*) --> "Initialization"

if "Some Test" then
  -->[true] "Some Activity"
  --> "Another activity"
  -right-> (*)
else
  ->[false] "Something else"
  -->[Ending process] (*)
endif
'
x <- plantuml(
  x
)
```

## Plot via vector format
Now we plot in in a device using vector format (svg) as intermediate format, which is the default

```{r exampleDeviceVector}
plot(
  x = x
# vector = TRUE
  )
```
